%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
\usepackage{hyperref} % For hyperlinks
\usepackage{lipsum}  

%----------------------------------------------------------------------------------------
%   DOCUMENT STARTS HERE
%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%   TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} 
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    
    {\fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Yash Siwach}}}} % First name
    
    \vspace{6pt}
    
    {\Large Developer $\sim$ Student} % Career or current job title
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    
    % The first parameter is the FontAwesome icon name, the second is the box size and the third is the text

  \icon{Phone}{11}{\href{tel:+917206099609}{+91-7206099609}}\\
  \icon{MapMarker}{11}{\href{https://maps.google.com/maps?q=Chandigarh,+India}{Chandigarh, India}}\\

    
\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
    \vspace{-\baselineskip} % Required for vertically aligning minipages
    
    \icon{Envelope}{11}{\href{mailto:Iamyashsiwah@gmail.com}{Iamyashsiwah@gmail.com}}\\   
    \icon{Github}{11}{\href{https://github.com/Iamyashsiwach}{Iamyashsiwach}}\\
    \icon{LinkedinSquare}{11}{\href{https://www.linkedin.com/in/yash-siwach}{Yash Siwach}}\\    
    
\end{minipage}


%----------------------------------------------------------------------------------------
%   INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------
\vspace{-11pt}
\begin{minipage}[t]{0.45\textwidth} % Adjusted width to prevent overlap
    \cvsect{Summary}
  \\
I am a student developer skilled in mobile (iOS, Swift), web development, and UI/UX design, dedicated to crafting user-centric experiences through my projects. I have practical expertise with Unity, Xcode, Figma, and various other tools. Currently pursuing a Bachelor's in Computer Applications (AR-VR), I am actively broadening my knowledge in areas such as cybersecurity and databases to stay current with industry trends.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
    \cvsect{Skills}
   
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Languages:}
        \vspace{-2pt}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
        Swift, C\#, HTML5, CSS3, JavaScript, PHP, SQL, LaTeX  
    \end{minipage}

    \vspace{8pt} % Adjust the vertical space as needed
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Technologies:}
        \vspace{-2pt}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
        SwiftUI, MySQL, DBMS, Git, Unity, Xcode, Figma, Adobe XD, Node.js
    \end{minipage}
    
    \vspace{8pt} % Adjust the vertical space for soft skills
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Soft Skills:}
        \vspace{-2pt}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
       Leadership, Teamwork, Problem-solving, Time Management, Adaptability, \\Creativity, Critical Thinking, Multitasking
    \end{minipage}
    
\end{minipage}


%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-2pt}
\cvsect{Education}
\begin{entrylist}
    \entry
        {\textbf{2022 - 2025}}
        {Bachelor of Computer Applications (AR-VR)}
        {Graduation}
        {Chandigarh University}
    \entry
        {\textbf{2022}}
        {Class 12th CBSE}
        {School}
        {DAV Public School, Thermal Colony, Panipat}
\end{entrylist}

%----------------------------------------------------------------------------------------
%   EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-22pt}
\cvsect{Experience}
\begin{entrylist}
    \entry
        {\textbf{02/2023 -- \\Present}}
        {\textbf{Vice President}}
        {Smile Foundation Society NGO}
        {\vspace{-10pt}
            \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=-1pt]
                \item Leading multifaceted social initiatives and orchestrating community empowerment projects.
                \item Demonstrating leadership by collaborating with stakeholders for impactful organizational goals.
            \end{itemize}
        }
    \entry
        {\textbf{02/2023 --\\03/2024}}
        {\textbf{ACM Student Member}}
        {Association for Computing Machinery}
        {\vspace{-10pt}
            \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=-1pt]
                \item Contributed to team initiatives, developing leadership and event management skills.
                \item Organized and executed events, fostering a vibrant community.
            \end{itemize}
        }
    \entry
        {\textbf{03/2023 -- \\05/2023}}
        {\textbf{UI/UX Design Intern}}
        {Imigrom Mediatech}
        {\vspace{-10pt}
            \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=-1pt]
                \item Acquired practical UI/UX design experience.
                \item Proficient in Figma and Adobe XD for creating intuitive interfaces, with a solid grasp of UI design concepts.
            \end{itemize}
        }
\end{entrylist}

%----------------------------------------------------------------------------------------
%   PROJECTS
%----------------------------------------------------------------------------------------
\vspace{-22pt}
\cvsect{Projects}

\begin{entrylist}
    \entry
        {\textbf{IoT}}
        {Portable Air Quality Index Monitor}
        {\href{https://www.linkedin.com/posts/yash-siwach_iot-airquality-smarthome-activity-7207296630738341889-wHXx?utm_source=share&utm_medium=member_desktop}{Link - Linkedin}}
        {\vspace{-\topsep} % Reduce space between title and first item
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=-1pt]
            \item Developed a Portable Air Quality Index (AQI) Monitor using Arduino technology and an MQ-135Hz sensor.
            \item Integrated Bluetooth connectivity and a real-time display for household air quality monitoring.
        \end{itemize}}
    \entry
        {\textbf{Unity}}
        {Unity AR Dragon Game}
        {\href{https://www.linkedin.com/feed/update/urn:li:activity:7193535905696018432/}{Link - Linkedin}}
        {\vspace{-\topsep} % Reduce space between title and first item
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=-1pt]
            \item Developed immersive AR game in Unity C\# with dynamic joystick controls.
            \item Ported game to iOS using Xcode, showcasing Unity, C\#, AR expertise.
        \end{itemize}}
    \entry
        {\textbf{Web Development}}
        {Website}
        {\href{https://github.com/Iamyashsiwach/SmileFoundationSociety_website.git}{Link - Github}}
        {\vspace{-\topsep} % Reduce space between title and first item
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=-1pt]
            \item Developed feature-rich NGO website with donation portals, event calendars, and volunteer forms.
            \item Ensured user-friendly interfaces and optimized performance for enhanced usability.
        \end{itemize}}
    \entry
        {\textbf{iOS Development}}
        {HappyBird - iOS Game Development}
        {\href{https://github.com/Iamyashsiwach/HappyBird}{Link - Github}}
        {\vspace{-\topsep} % Reduce space between title and first item
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=-1pt]
            \item Created HappyBird, an iOS game inspired by Flappy Bird.
            \item Implemented intuitive tap controls, dynamic obstacle generation, and vibrant graphics.
        \end{itemize}}
\end{entrylist}


%----------------------------------------------------------------------------------------
%   CERTIFICATIONS
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%   CERTIFICATIONS
%----------------------------------------------------------------------------------------
\vspace{-20pt}
\cvsect{Certifications}
\begin{entrylist}\vspace{-6pt}
    \entry 
       {\textbf{02/2023}}
        {iOS Swift - The Complete iOS App Development Bootcamp}
        {}
        {Udemy}
        \vspace{-6pt}
    \entry
       {\textbf{08/2023}}
        {Introduction to Cyber Attacks}
        {\href{https://coursera.org/verify/8W8PWE46S26X}{Link - Certification}}
        {New York University}
        \vspace{-6pt}
    \entry
       {\textbf{08/2023}}
        {Principles of UX/UI Design by Meta}
        {\href{https://coursera.org/verify/WCEKDRQCCW4B}{Link - Certification}}
        {Meta}
    \entry
       {\textbf{04/2024}}
        {Clean Data in SQL using MySQL Workbench}
        {\href{https://coursera.org/verify/XGVP9YAUKMXT}{Link - Certification}}
        {Coursera}
        \vspace{-6pt}
    \entry
       {\textbf{04/2024}}
        {Using MySQL Database with PHP}
        {\href{https://coursera.org/verify/XMQ936YYLDE3}{Link - Certification}}
        {Coursera}
        \vspace{-6pt}
    \entry
       {\textbf{04/2024}}
        {Build a MERN application using Next.js}
        {\href{https://coursera.org/verify/HQUKBXN7T99S}{Link - Certification}}
        {Coursera}
\end{entrylist}


%----------------------------------------------------------------------------------------
%   END DOCUMENT
%----------------------------------------------------------------------------------------
\end{document}
